---
title: "March FR - COVID-19"
author: "Dilay Ercelik"
date: "07/04/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
AUTHOR : Dilay Ercelik (07/04/2020)

This R Markdown visually presents the number of new cases and the number of new deaths by day, throughout the month of March (2020), in the country of France.

The raw data (covid_19 dataset) comes from the European Centre for Disease Prevention and Control, available online at https://data.europa.eu/euodp/en/data/dataset/covid-19-coronavirus-data/resource/55e8f966-d5c8-438e-85bc-c7a5a26f4863 

All other datasets originate from this initial extensive dataset.

```{r}
library(tidyverse)

covid_19 <- read.csv("COVID-19-geographic-disbtribution-worldwide.csv")
```

```{r}
march_FR_C19 <- france_19 %>% filter(month == "March")
```

```{r}
ggplot(march_FR_C19, aes(x = day, y = n_new_cases))+ 
  geom_line()+
  geom_point(color = "red", size = 2)+
  theme_bw()+
  labs(x ="Day", y ="Number of New Cases", title ="Number of New Cases by Day throughout the Month of March (France, 2020)", subtitle = "Data from the European Centre for Disease Prevention and Control ")
```
SEE PLOT C


```{r}
ggplot(march_FR_C19, aes(x = day, y = n_new_deaths))+ 
  geom_line()+
  geom_point(color = "red", size = 2)+
  theme_bw()+
  labs(x ="Day", y ="Number of New Deaths", title ="Number of New Deaths by Day throughout the Month of March (France, 2020)", subtitle = "Data from the European Centre for Disease Prevention and Control ")

```
SEE PLOT D







